### 2010-10-12 papers/BMD2010/PhysicalParametersPaper/paper.tex
the bicycle descriptions are good

\begin{center}
\fontsize{14}{20}{\bf Accurate Measurement of Bicycle Parameter[3pt]}
\end{center}

%%%%%%%%%%%%%%%% authors %%%%%%%%%%%%%%%
\begin{center}
\normalsize{\bf{Jason K. Moore$^{*}$, Mont Hubbard, A. L. Schwab$^\#$,
            J. D. G. Kooijman$^\dag$}}
\end{center}

\begin{center}
\begin{tabular}{c}
$^*$ Mechanical and Aerospace Engineering\\
University of California, Davis\\
One Shields Avenue, Davis, CA, 95616, USA\\
e-mail: jkmoor@ucdavis.edu, mhubbard@ucdavis.edu\\
\end{tabular}
\begin{tabular}{c}
$^\#$ Laboratory for Engineering Mechanics\\
Delft University of Technology\\
Mekelweg 2, 2628CD Delft, The Netherlands\\
e-mail: a.l.schwab@tudelft.nl, jodikooijman@gmail.com\\
\end{tabular} \\ \vspace{2.5ex}

@@

\section{Bicycle Descriptions}
\begin{description}
    \item[Batavus Browser]{The Batavus Browser is lower priced Dutch city bike.
        We measured the physical proprieties of the stock Browser model and
        also the same bike with the instrumentation used in our experiments.}
    \item[Batavus Crescendo Deluxe]{The Batavus Crescendo Deluxe is a
        contemporary of all-round cycling in cool black and white. A great bike
        for a good end to touring. And that works fine with 8 gears, suspension
        fork and suspension seatpost.}
    \item[Gary Fisher Mountain Bike]{The Gary Fisher Ziggurat is a modern front
        suspended mountain bike.}
    \item[2007 Bianchi Pista]{The Pista is a modern steel track bicycle.}
    \item[Batavus Stratos Deluxe]{Is a Dutch sport bicycle.}
    \item[Yellow Bicycle]{The yellow is a bicycle used in the lab to
        demonstrate that a bicycle is stable at certain speeds. It is an
        aluminum road frame of unknown make with the majority of components
        removed. The wheels, drop handlebar, seat, seat post and bottom bracket
        are the only parts on the bike. The fork has been reversed to
        ''increase``~\cite{Kooijman2006} the stability of the bicycle. The
        bicycle was measured with both the fork in normal position and the fork
        reversed.}
\end{description}
\begin{figure}[htbp]
    \centering
    \subfloat[Batavus Browser]{
        \label{fig:browser}\includegraphics[width=1.75in]{../../../images/browserIns_sub.jpg}}
    \subfloat[Batavus Crescendo Deluxe]{
        \label{fig:crescendo}\includegraphics[width=1.75in]{../../../images/crescendo_sub.jpg}}
    \subfloat[Gary Fisher]{
        \label{fig:fisher}\includegraphics[width=1.75in]{../../../images/fisher_sub.jpg}}
        \\
    \subfloat[Bianchi Pista]{
        \label{fig:pista}\includegraphics[width=1.75in]{../../../images/pista_sub.jpg}}
    \subfloat[Batavus Stratos Deluxe]{
        \label{fig:stratos}\includegraphics[width=1.75in]{../../../images/stratos_sub.jpg}}
    \subfloat[Yellow Bicycle]{
        \label{fig:yellow}\includegraphics[width=1.75in]{../../../images/yellow_sub.jpg}}
    \caption{The six bicycles measured in the experiments. The Batavus
    Browser~\subref{fig:browser} is shown with the instrumentation and the
    Yellow Bicycle~\subref{fig:yellow} is shown with its fork reversed.}
    \label{fig:bicycles}
\end{figure}
\section{Accuracy}
Error propagation theory was utilized to calculate what the accuracy the
benchmark ideal parameters are based on the measurements taken. If $x$ is a
random variable and is defined as $x=f(u,v,\ldots)$ then the sample variance of
$x$ is defined as
\begin{equation}
    s_x^2 = \frac{1}{N-1}\sum^N_{i=1}
    \left[(u_i - \bar{u})^2\left(\frac{\partial x}{\partial u}\right)^2 +
    (v_i - \bar{v})^2\left(\frac{\partial x}{\partial v}\right)^2 +
    2(u_i - \bar{u})(v_i - \bar{v})\left(\frac{\partial x}{\partial u}\right)\left(\frac{\partial x}{\partial v}\right)
    + \ldots\right]
    \label{eqn:sampleVariance}
\end{equation}
Using the definitions for variance and covariance
Equation~\ref{eqn:sampleVariance} can be simplified to
\begin{equation}
    s_x^2 = s_u^2\left(\frac{\partial x}{\partial u}\right)^2 +
            s_v^2\left(\frac{\partial x}{\partial v}\right)^2 +
            2s_{uv}\left(\frac{\partial x}{\partial u}\right)\left(\frac{\partial x}{\partial v}\right)
            + \ldots
    \label{eqn:variance}
\end{equation}
If $u$ and $v$ are uncorrelated then $s_{uv}=0$. We assume that the all the
random variables hereafter are uncorrelated. Equation~\ref{eqn:variance} can be
used to calculated the variance of all types of functions. The most basic are
functions such as addtion
\begin{eqnarray}
    \label{eqn:addition}
    x &=&  au + bv\\
    s_x &=& a^2s_u^2 + b^2s_v^2
\end{eqnarray}

>>>>

\begin{center}
\fontsize{14}{20}{\bf Accurate Measurement of Bicycle Parameters}
\end{center}

%%%%%%%%%%%%%%%% authors %%%%%%%%%%%%%%%
\begin{center}
\normalsize{\bf{Jason K. Moore$^{*}$, Mont Hubbard$^{*}$, A. L. Schwab$^\dag$,
            J. D. G. Kooijman$^\dag$}}
\end{center}

\begin{center}
\begin{tabular}{c}
$^*$ Mechanical and Aerospace Engineering\\
University of California, Davis\\
One Shields Avenue, Davis, CA, 95616, USA\\
e-mail: jkmoor@ucdavis.edu, mhubbard@ucdavis.edu\\
\end{tabular}
\begin{tabular}{c}
$^\dag$ Laboratory for Engineering Mechanics\\
Delft University of Technology\\
Mekelweg 2, 2628CD Delft, The Netherlands\\
e-mail: a.l.schwab@tudelft.nl, jodikooijman@gmail.com\\
\end{tabular} \\ \vspace{2.5ex}

@@

\section{Bicycle Descriptions}
We choose to measure the physical parameters of six bicycles
Figs.~\ref{fig:bicycles}. The three Batavus bicycles were donated by the
manufacturer. We asked for a bicycle that they considered stable and one that
they did not. They claimed the Browser was a ``stable'' bicycle and that the
Stratos was ``nervous''. The Fisher and the Pista were chosen to provide some
variety, a mountatin and road bike. The yellow bike is used to demonstrate
bicycle stability.
\begin{description}
    \item[Batavus Browser]{The Batavus Browser Fig.~\ref{fig:browser} is an averaged priced Dutch city
        bike. It has a steel frame, a three speed internal rear hub, handle
        bars for an upright posture and includes various accerories for utility
        puposes. We measured the physical proprieties of the stock Browser model and
        also equipped with the instrumentation used in our other
        experiments~\cite{Kooijman2009}.}
    \item[Batavus Crescendo Deluxe]{The Batavus Crescendo Deluxe
        Fig.~\ref{fig:crescendo} is also a
        Dutch city bike that is setup for touring. It has an aluminum frame, an
        eight speed internal hub, upright handlebars, accesories for utility
        and a suspension fork and suspension seatpost.}
    \item[Gary Fisher Ziggurat]{The Gary Fisher Ziggurat Fig.~\ref{fig:fisher} is a modern
        lightweight front suspended mountain bike. It has a ?? frame, large low
        pressure mountain bike tires, and is setup for racing with few extra accerories.}
    \item[2007 Bianchi Pista]{The Bianchi Pista Fig.~\ref{fig:pista} is a modern lightweight steel track
        bicycle. It has a single gear ratio and minimal extras to keep the
        weight low. It has drop handlebars and high pressure racing tires.}
    \item[Batavus Stratos Deluxe]{The Batavus Stratos Deluxe
        Fig.~\ref{fig:stratos} is a sporty Dutch city bicycle. The frame is
        made of aluminum and it has a seven speed internal hub. It has mountain
        style handle bars for a less upright seating posture, but also includes
        accesories for utility such as a rear rack, fenders, light and
        chainguard.}
    \item[Yellow Bicycle]{The yellow bicycle Fig.~\ref{fig:yellow} used in the lab to
        demonstrate that a bicycle is stable at certain speeds. It is an
        aluminum road frame of unknown make with the majority of components
        removed. The wheels, drop handlebar, seat, seat post and bottom bracket
        are the only parts on the bike. The bicycle was measured with both the
        fork in normal position and the fork reversed. The fork was reversed to
        ''decrease the minimal stable speed``~\cite{Kooijman2006} of the bicycle.}
\end{description}
    \subfloat[Batavus Browser]{
        \label{fig:browser}\includegraphics[width=1.75in]{../../../images/browserIns_sub.jpg}}
    \subfloat[Batavus Crescendo Deluxe]{
        \label{fig:crescendo}\includegraphics[width=1.75in]{../../../images/crescendo_sub.jpg}}
    \subfloat[Gary Fisher]{
        \label{fig:fisher}\includegraphics[width=1.75in]{../../../images/fisher_sub.jpg}}
        \\
    \subfloat[Bianchi Pista]{
        \label{fig:pista}\includegraphics[width=1.75in]{../../../images/pista_sub.jpg}}
    \subfloat[Batavus Stratos Deluxe]{
        \label{fig:stratos}\includegraphics[width=1.75in]{../../../images/stratos_sub.jpg}}
    \subfloat[Yellow Bicycle]{
        \label{fig:yellow}\includegraphics[width=1.75in]{../../../images/yellow_sub.jpg}}
    \caption{The six bicycles measured in the experiments. The Batavus
    Browser~\subref{fig:browser} is shown with the instrumentation and the
    Yellow Bicycle~\subref{fig:yellow} is shown with its fork reversed.}
    \label{fig:bicycles}
\section{Accuracy}
Error propagation theory was utilized to calculate what the accuracy the
benchmark ideal parameters are based on the measurements taken. If $x$ is a
random variable and is defined as $x=f(u,v,\ldots)$ then the sample variance of
$x$ is defined as
    s_x^2 = \frac{1}{N-1}\sum^N_{i=1}
    \left[(u_i - \bar{u})^2\left(\frac{\partial x}{\partial u}\right)^2 +
    (v_i - \bar{v})^2\left(\frac{\partial x}{\partial v}\right)^2 +
    2(u_i - \bar{u})(v_i - \bar{v})\left(\frac{\partial x}{\partial u}\right)\left(\frac{\partial x}{\partial v}\right)
    + \ldots\right]
    \label{eqn:sampleVariance}
Using the definitions for variance and covariance
Equation~\ref{eqn:sampleVariance} can be simplified to
    s_x^2 = s_u^2\left(\frac{\partial x}{\partial u}\right)^2 +
            s_v^2\left(\frac{\partial x}{\partial v}\right)^2 +
            2s_{uv}\left(\frac{\partial x}{\partial u}\right)\left(\frac{\partial x}{\partial v}\right)
            + \ldots
    \label{eqn:variance}
If $u$ and $v$ are uncorrelated then $s_{uv}=0$. We assume that the all the
random variables hereafter are uncorrelated. Equation~\ref{eqn:variance} can be
used to calculated the variance of all types of functions. The most basic are
functions such as addtion
\begin{eqnarray}
    \label{eqn:addition}
    x &=&  au + bv\\
    s_x &=& a^2s_u^2 + b^2s_v^2
\end{eqnarray}
